### 2020-04-26 README.Rmd
Add examples to functions

The worcs logo makes use of the gear, services, gears, preferences, settings icon, made by MD Badsha Meah from www.freeicons.io.

>>>>

The worcs logo is inspired by the Open Science Badges by the Center for Open Science (CC-BY-4.0), and makes use of the gear, services, gears, preferences, settings icon, made by MD Badsha Meah from www.freeicons.io (CC-BY-3.0).
